---
title: "Hello, R"
subtitle: "An example Quarto post with executable R code."
date: "2026-05-14"
categories: [r, tidyverse, example]
format:
  html:
    code-fold: false
---

This post is an **`.Rmd` file** rendered by Quarto. Same chunk syntax you
know from Rmarkdown — Quarto picks up the `knitr` engine automatically
when it sees R chunks.

## A tiny dataset

```{r}
#| message: false
library(tibble)
library(dplyr)

sales <- tibble(
  month   = seq(as.Date("2026-01-01"), by = "month", length.out = 6),
  revenue = c(120, 138, 155, 162, 180, 205),
  channel = "organic"
)
sales
```

## A quick plot

```{r}
#| message: false
#| fig-width: 6
#| fig-height: 3.5
library(ggplot2)

ggplot(sales, aes(month, revenue)) +
  geom_line() +
  geom_point(size = 2) +
  labs(title = "Monthly revenue, organic channel",
       x = NULL, y = "Revenue ($k)") +
  theme_minimal()
```

## Notes

- Quarto renders `.Rmd` files the same way it renders `.qmd` files with R
  chunks. If you prefer the newer Quarto syntax, just rename the file to
  `index.qmd`.
- Use chunk options as YAML-style `#|` comments (Quarto convention), or
  the classic inline `{r, fig.width=6}` form — both work.
